Notes and approaches to OCR

### 2020-12-09 outputs/documents/paper.Rmd
Begin updating paper

---
title: "Notes and approaches to OCR"
author: "Rohan Alexander, John Tang, Diego Mamanche Castellanos"
date: "8 December 2020"
abstract: "TBD"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
bibliography: references.bib
---

@@

```{r echo=FALSE, include=FALSE, warning=FALSE}
library("reticulate")
```

@@

A crucial step in the data analysis workflow is gathering data. This step involves tools and methods to collect raw data in an systematic way. In this paper we are interested in gathering data from Portable Document Format (PDF) files, in particular, when these PDFs were created by scans, and hence must be processed before their data can be analysed. Such PDF files are unstructured data, meaning that the data are not tagged and are not organised in a regular way.^[Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset. Some examples are tables and relations. Semi-structured data contains this same information, but instead of having regular structures applied to all items in the dataset, the data might be interpreted with structural information. It can be supplied as tags e.g. name = "Bob" but also other markers to separate semantic elements and enforce hierarchies of records and fields within the data. Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags. However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data [@Losee2006]. This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags could be assigned manually, typically a statistical model is used for reasons of efficiency, and this process is called Optical Character Recognition (OCR). We evaluate several pre-trained commercial OCR options accessed via APIs: 1) X, 2), and 3), ; additionally several OCR options that are run locally: 4) X, 5), and 6), ; and finally 7) training our own model. We find... **[TBD]**.

PDF files were developed in 1993 by the technology company Adobe and are useful for documents because they should display in a consistent way independent of the environment that created them or the environment in which they are being viewed. One feature of PDFs is that they can include a variety of objects, for instance, text, photos, figures, etc. However, this variety can limit the capacity of PDFs to be used directly as data inputs for statistical analysis. The data first needs to be extracted from the PDF.

Sometimes it is possible to copy and paste the data from the PDF. This is more likely when the PDF only contains simple text or regular tables. In particular, if the PDF has been created by an application such as Word then often the text can be extracted in this way because they are stored as text. But it is not as easy if the text has been stored as an image which is then part of the PDF

Furthermore, there is a linguistic component that adds more complexity. For instance, it is well known that non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[ADD CITE]**. It is because those characters have complicated structures, a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji), and resemblance among characters, font unevenness, or writing styles. In those cases, the need for reliable tools or methods with the ability to elicit data becomes extremely important.

Optical character recognition (OCR),is a process that transforms a bitmapped image of printed or handwritten text into text code **[ADD CITE]**. It thereby becomes machine-readable. It has been used to parse images of characters since the 1950s **[ADD CITE]**. These initial approaches used mechanical and optical means of rotating disks and photomultiplier flying spot scanner with a cathode ray tube lens, followed by photocells and arrays of them **[ADD CITE]**. The OCR process was slow, and one line of characters could be digitized at a time. These days once a printed or handwritten text has been captured optically by a scanner or some other optical means, the digital image goes through the following stages of a computer recognition system [@Cheriet2007]:

- The preprocessing stage that enhances the quality of the input image and locates
the data of interest.
- The feature extraction stage that captures the distinctive characteristics of the
digitized characters for recognition.
- The classification stage that processes the feature vectors to identify the characters and words.

In this paper we review various OCR options for researchers who need to gather data from PDFs in which the text must be extracted to be reused, edited, or reformatted; the text should be available for full-text information retrieval; the text is to be coded in HTML or SGML; the text should be available to adaptive equipment for the visually impaired; the file size is of concern (in terms of storage or bandwidth to transmit); or the resources are available to perform OCR and correct the output.

Although this step remains the same regardless of the field of study, the methods used vary between those fields of study because of their different interests. Moreover, the diversity of data types adds complexity to the process of gathering data.

**When they consider a primer on what OCR options exist these days depending on your technical ability and then how they perform for an easy example and then how they perform for a hard example (the Japanese extract) and finally some suggestions for what is needed in the future....**

**Our paper represents...**

**The remainder of this paper is structured as follows...**

@@

## Test Samples

Japanese dictionaries...[Rohan]

For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the selected OCR tools. The image contains 3293 characters. Words in English were counted as one character for this analysis. MOreover, the sample text was divided into four images called **sections** as illustrated in Figure \@ref(fig:sections). These new images were assessed across all OCR tools.

@@

This example is in a vertical form, meaning that it should be read it from right to left and from the top to the bottom. This is important since it is expected to obtain from each OCR tool the correct sequence of characters. For instance, from section 1 in figure xx, the first five characters from the first line are **[一本の傘を]**. We expect to see the same sequence from each OCR tool.

@@

## OCR options

The following list contains the OCR APIs and libraries available that will be evaluated in this study:

| OCR Tool                             | Company	 | Type           |	Monthly Price Aug/2020 |	Tech Requierements |
| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
| Azure Cognitive Services (OCR)       | Microsoft | API		        | Free Web Container: 5000/Free; <br/> <br/> S1 Web Container: 0-1M/$1.50 per 1,000 trans, 1M-5M/$1 per 1,000 trans, 5M-10M/$0.65 per 1,000 trans, 10M-100M/$0.65 per 1,000 trans, +100M/$0.65 per 1,000 trans        |                    |
| Amazon Rekognition	                 | Amazon	   | API		        | First 1 million images: $0.001 per image <br/> <br/> Next 9 million images $0.0008 per image <br/> <br/> Next 90 million images $0.0006 per image <br/> <br/> Over 100 million images $0.0004 per image         |                    |
| PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
Standard: $0.002 per trans      |                    |
| Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
| Google Vision (for Text recognition) | Google	   | API		        | 1000/Free, 5 mill/$1.5, >5mill/$0.6        |                    |
| Amazon Textract	                     | Amazon	   | API		        | First 1 Million pages: $0.015 - $0.05 per page, <br/> <br/> Over 1 Million pages: $0.01 - $0.04 per page        |                    |
|	Kindai-OCR                           | Result of n2i Project    | Python Library | Free    |                    |

>>>>

---
title: "Notes and approaches to OCR"
author: "Rohan Alexander, John Tang, Diego Mamanche Castellanos"
date: "8 December 2020"
abstract: "TBD"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: false
bibliography: references.bib
---

@@

```{r echo=FALSE, include=FALSE, warning=FALSE}
library(reticulate)
library(tidyverse)
```

@@

A crucial step in the data analysis workflow is gathering data. This step involves tools and methods to collect raw data in an systematic way. In this paper we are interested in gathering data from Portable Document Format (PDF) files, in particular, when these PDFs were created by scans, and hence must be processed before the data they contain can be prepared, cleaned, and analysed. Such PDF files are generally unstructured data, meaning that the data are not tagged nor organised in a regular way.^[Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset. Some examples are tables and relations. Semi-structured data contains this same information, but instead of having regular structures applied to all items in the dataset, the data might be interpreted with structural information. It can be supplied as tags e.g. name = "Bob" but also other markers to separate semantic elements and enforce hierarchies of records and fields within the data. Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags. However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data [@Losee2006]. This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags in the form of a text replacement for each character image could be assigned manually, typically a statistical model is used for reasons of efficiency and reproducibility, and this process is called Optical Character Recognition (OCR). We evaluate several pre-trained commercial OCR options accessed via APIs: 1) X, 2), Y and 3) Z; additionally several pre-trained OCR options that we run ourselves: 4) X, 5), Y and 6) Z ; and finally 7) training and running our own model. We find... **[TBD]**.

PDF files were developed in 1993 by the technology company Adobe and are useful for documents because they are meant to display in a consistent way independent of the environment that created them or the environment in which they are being viewed. A PDF viewed on an iPhone should look the same as on a Android phone, as on a Linux desktop. One feature of PDFs is that they can include a variety of objects, for instance, text, photos, figures, etc. However, this variety can limit the capacity of PDFs to be used directly as data inputs for statistical analysis. The data first needs to be extracted from the PDF.

Sometimes it is possible to copy and paste the data from the PDF. This is more likely when the PDF only contains simple text or regular tables. In particular, if the PDF has been created by an application such as Microsoft Word, or another document or form creation system, then often the text data can be extracted in this way because they are actually stored as text within the PDF. But it is not as easy if the text has been stored as an image which is then part of the PDF. This may be the case for PDFs produced through scans or photos of physical documents, and some older document preparation software.

**[DIEGO - where is this coming from?]** Furthermore, there is a linguistic component that adds more complexity. For instance, non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[DIEGO - add cite]**. Not only do these languages have complicated structures and a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji). But often many characters are similar and fonts may have a large effect **[DIEGO - add cite]**. In those cases, the need for reliable approaches to replace an image containing many characters with text of those characters becomes important.

Optical character recognition (OCR) is a process that transforms a image of text into actual text. Although there may not be much difference to a human reading a PDF before and after OCR, the main difference is that the PDF is now machine-readable **[DIEGO - add cite]**. OCR has been used to parse images of characters since the 1950s, initially using physical processes **[DIEGO - add cite]**. Such approaches were understandably slow and have been replaced by a computer-based recognition system involving the following steps [@Cheriet2007 p. X]:

- Pre-processing to both: increase the quality of the input image, and to focus on the data of interest.
- Feature extraction to identify the distinctive features of the characters to be recognized.
- The actual classification stage, in which those features are used to identify the characters.

In this paper we review various OCR options for data analysts who need to gather their data from PDFs where the characters of interest for analysis must first be transformed from image to text. The paper goes through the process of using various options to do this OCR and the tradeoffs that must be made. We consider a few different options in terms of the image that is to be transformed. We start with a one page extract of modern English, a one-page table of numbers, one page of modern Japanese, one page from an English book from the 1800s, and a page from a Japanese dictionary from the early 1900s.

We find... **[TBD]**.

The remainder of this paper is structured as follows... **[TBD]**. Finally we make some suggestions for what is needed in the future.

**DIEGO - what is this?**.
; the text should be available for full-text information retrieval; the text is to be coded in HTML or SGML; the text should be available to adaptive equipment for the visually impaired; the file size is of concern (in terms of storage or bandwidth to transmit); or the resources are available to perform OCR and correct the output.

# Background

In this section we introduce the OCR options that we consider, they essential features and cost.

There are seven OCR options evaluated in this study (Table \@ref(tab:tableofoptions)).

```{r tableofoptions, echo=FALSE, warning = FALSE, message = FALSE}
options <- read_csv(here::here("inputs/ocr_options.csv"))
options %>% 
  knitr::kable(booktabs = TRUE, 
               caption = "OCR options",
               )

**Add paragraph about each.**

@@

## Modern English

**TBD.**

## Table of numbers

**TBD.**

## Modern Japanese

**TBD.**

## English book from the 1800s

**TBD.**

## Japanese dictionaries from the early 1900s

For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the selected OCR tools. The image contains 3293 characters. Words in English were counted as one character for this analysis. Moreover, the sample text was divided into four images called **sections** as illustrated in Figure \@ref(fig:sections). These new images were assessed across all OCR tools.

@@

This example is in a vertical form, meaning that it should be read it from right to left and from the top to the bottom. This is important since it is expected to obtain from each OCR tool the correct sequence of characters. For instance, from section 1 in Figure \@ref(fig:section1), the first five characters from the first line are **[一本の傘を]**. We expect to see the same sequence from each OCR tool.

@@

# Results
